### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon _ Enthaply - put in draft paragraph

Target error plot?

>>>>

The deconvolution fits were integrated to find the area under each curves. This information provides the \gls{h} of the crystallization of each phase. This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively. Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.
